Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-05 article.tex
wording

%     4/ non-linear filter based on the neuron activations

\begin{enumerate}[i.]
\item A non-linear filter: we re-weight samples depending on the current
      activity of the systems in order to favour the association measure when
      directly connected neurons are firing together, while artificially
      reducing the association measure in case of extreme network activity,
      i.e. high when a network firing is happening and low when no neuron is
      active.
\end{enumerate}

>>>>

Then we apply a non-linear filter based on the current
activity of the systems in order to favour the association measure when
directly connected neurons are firing together, while artificially
reducing the association measure in case of extreme network activity,
i.e. high when a network firing is happening and low when no neuron is
active.
